Price of Anarchy for Mean Field Games

### 2018-07-03 PoA.tex
addressed minor points 1-3, 5, 7-9, 11-13

We consider a system of $N$ players whose private states are denoted at time $t$ by $X^1_t$, $X^2_t$, $\cdots$, $X^N_t$. To keep the presentations simple, we assume the state space is $\mathbb{R}$. We denote by $\mu^N_t$ the empirical distribution of the states, namely
\begin{equation*}
\mu^N_t=\frac1N\sum_{i=1}^N\delta_{X^i_t}.
\end{equation*}
We assume that these states evolve in continuous time under the influences of controls  $\alpha^1_t$, $\alpha^2_t$, $\cdots$ , $\alpha^N_t$ $\in \mathbb{A}$, where the set of admissible controls, $\mathbb{A}$, will be defined later. Let $\nu^N_{t}$ denote the empirical measure of the controls:
\begin{equation*}
\nu^N_t=\frac1N\sum_{i=1}^N\delta_{\alpha^i_t}.
\end{equation*}
We also assume that if and when interactions between these states and controls are present, they are of a mean field type, i.e. through $\mu^N_t$ and $\nu^N_t$. The time evolution of the state for player $i$ is given by the It\^{o} dynamics:
\begin{equation*}
    dX^i_t=b(t,X^i_t,\mu^N_t,\alpha^i_t,\nu^N_t)dt+\sigma dW_t.
\end{equation*}
We work over the interval $[0,T]$ limited by a finite time horizon $T \in \mathbb{R}^+$. We assume the drift function $b(t,x,\mu,\alpha,\nu): [0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A})  \rightarrow \mathbb{R}$ is Lipschitz in each of it's inputs. For the sake of simplicity, we assume that the volatility, $\sigma$, is a positive constant.

\subsubsection*{\textbf{Cost Functionals}}
We assume that we are given two functions $f(t,x,\mu,\alpha, \nu): [0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A}) \rightarrow \mathbb{R}$ and $g(x,\mu):\mathbb{R}\times \cP(\mathbb{R}) \rightarrow \mathbb{R}$ which we call running and terminal cost functions, respectively. We assume $f$ and $g$ are Lipschitz in each of it's arguments. The goal of player $i$ is to minimize its expected cost as given by:
\begin{equation*}
J^i(\balpha^1,\cdots,\balpha^N)=\EE\bigg[\int_0^Tf(t,X^i_t,\mu^N_{t},\alpha^i_t,\nu^N_{t})\,dt +g(X^i_T,\mu^{N}_{T})\bigg].
\end{equation*}

@@

\subsection{\textbf{Nash Equilibrium: Mean Field Game Formulation}}
\label{sub:MFG_formulation}
The goal of this subsection is to articulate what is meant by a feedback function providing a mean field game equilibrium. To begin, we define what we call the \textit{mean field environment}. By symmetry of the players, we suppose all of the players in the mean field use the same feedback function, $\phi$. Then the \textit{mean field environment} specified by $\phi$ is characterized by $\cL(X^{\phi}_t)_{0\le t\le T}$ and $\cL(\phi(t,X^{\phi}_t))_{0\le t\le T}$ where the dynamics of $(X^{\phi}_t)_{0\le t\le T}$ are given by equation (\ref{eq:X}). Since we search for a Nash equilibrium, we consider a representative agent who wishes to find their best response, $\phi'$, to the mean field environment specified by $\phi$, in which case their state is given by $\boldsymbol{X^{\phi',\phi}}=(X^{\phi',\phi}_t)_{0\le t\le T}$ solving the standard stochastic differential equation:
\begin{equation*}
    dX^{\phi',\phi}_t=b(t,X^{\phi',\phi}_t,\cL(X^{\phi}_t),\phi'(t,X^{\phi',\phi}_t),\cL(\phi(t,X^{\phi}_t))dt+\sigma dW_t.
\end{equation*}
Consider the function:
\begin{equation*}
    \cS(\phi',\phi)=\biggl[\int_0^T<f(t,\cdot,\cL(X^{\phi}_t),\phi'(t,\cdot),\cL(\phi(t,X^{\phi}_t)),\cL(X^{\phi',\phi}_t)> dt +<g(\cdot,\cL(X^{\phi}_T)),\cL(X^{\phi',\phi}_t)>\biggr].
\end{equation*}
The best response for the representative agent in the mean field environment specified by $\phi$ is the feedback function minimizing this cost, namely $\phi^*=\arg\inf_{\phi'}\cS(\phi',\phi)$. Assuming the minimizer is unique (which will be the case for the models we consider), this defines a mapping $\Phi:\phi \rightarrow \phi^*$. If there is a $\hat{\phi}$ such that $\Phi(\hat{\phi})=\hat{\phi}$, then the players are in a mean field game equilibrium.

Thus, the search for a feedback function providing a mean field game equilibrium can be summarized as the following set of two successive steps:
\begin{enumerate}
\item For each feedback function $\phi:[0,T] \times \mathbb{R} \rightarrow \mathbb{R}$, solve the optimal control problem
\begin{equation*}
    \phi^*=\arg \inf_{\phi'}\cS(\phi',\phi).
\end{equation*}
Define the mapping $\Phi:\phi \rightarrow \phi^*$.
\item Find a fixed point $\hat{\phi}$ of $\Phi$ such that $\Phi(\hat{\phi})=\hat{\phi}$.
\end{enumerate}

When these two steps can be taken successfully, we say that $\hat{\phi}$ provides a mean field game equilibrium. Note that $\boldsymbol{X^{\hat{\phi},\hat{\phi}}}=\boldsymbol{X^{\hat{\phi}}}$ and therefore $\cS(\hat{\phi},\hat{\phi})=SC(\hat{\phi})$ gives the social cost for the mean field game equilibrium provided by $\hat{\phi}$. Notice that there could possibly be many feedback functions providing a mean field game equilibrium. Let $\mathcal{N}$ denote the set of all such feedback functions providing mean field game equilibria, as detailed above, i.e.
\begin{equation*}
    \mathcal{N}=\{\phi:[0,T] \times \mathbb{R} \rightarrow \mathbb{R}: \Phi(\phi)=\phi \}.
\end{equation*}

@@

\begin{equation*}
\begin{split}
    dY_t&=- \partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)dt+Z_tdW_t \\
    Y_T&=\partial_xg(X_T, \cL(X_T)).
\end{split}
\end{equation*}
A sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,y)=0$. According to the Pontryagin stochastic maximum principle, we introduce the function:
\begin{equation*}
    \hat{\alpha}(t,x,\bar{\mu},\bar{\nu},y)=\frac{\bar{r}(t)\bar{s}(t)\bar{\nu}-b_2(t)y}{r(t)+\bar{r}(t)},
\end{equation*}
and use the control $\hat{\alpha}_t=\hat{\alpha}(t,x,\bar{\mu},\bar{\nu},Y_t)$. When solving the fixed point step, we identify $\bar{\nu}_t=\mathbb{E}(\hat{\alpha}_t)$. By taking the expectation, we find:
\begin{equation*}
    \mathbb{E}(\hat{\alpha}_t)=c^{MFG}(t)\mathbb{E}(Y_t)
\end{equation*}
with:
\begin{equation*}
    c^{MFG}(t)=-\frac{b_2(t)}{r(t)+\bar{r}(t)(1-\bar{s}(t))}.
\end{equation*}
Thus, necessarily we must have:
\begin{equation*}
    \hat{\alpha}_t=a^{MFG}(t) Y_t+b^{MFG}(t)\mathbb{E}(Y_t)
\end{equation*}
with:
\begin{equation*}
    a^{MFG}(t)=-\frac{b_2(t)}{r(t)+\bar{r}(t)},
\end{equation*}
and:
\begin{equation*}
    b^{MFG}(t)=-\frac{\bar{r}(t)\bar{s}(t)b_2(t)}{(r(t)+\bar{r}(t))(r(t)+\bar{r}(t)(1-\bar{s}(t)))}.
\end{equation*}
So the solution of the mean field game equilibrium problem is given by the solution to the FBSDE system:
\begin{equation}
\begin{split}
        dX_t&=\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MFG}(t)b_2(t)Y_t+(b^{MFG}(t)b_2(t)+c^{MFG}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
        dY_t&=-\left((q(t)+\bar{q}(t))X_t-\bar{q}(t)s(t)\mathbb{E}X_t+b_1(t)Y_t \right)dt +Z_t dW_t
\end{split}
\label{eq:FBSDE_EMFG}
\end{equation}
with initial condition $X_0=\xi$, a random variable with finite mean and variance, and terminal condition $Y_T=(q_T+\bar{q}_T)X_T-\bar{q}_Ts_T\mathbb{E}X_T$.

@@

\begin{proposition}
	Under assumption (\ref{eq:assumptions}), the difference in the social costs in the LQEMFG and LQEMKV problems can be represented by
	\begin{equation*}
		\Delta SC := SC^{MFG} - SC^{MKV} =  \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt.
	\end{equation*}
\label{prop:diff_SC}
\end{proposition}
\begin{proof}
	The solutions $\bar{\eta}^{MFG}_t$ and $\bar{\eta}^{MKV}_t$ for the associated Riccati equations are well defined under assumption (\ref{eq:assumptions}). We notice that $\Delta\bar{\eta}_t$ defined in (\ref{eq:delta_eta}) satisfies the following first-order differential equation:
	\begin{equation*}
		\frac{d( \Delta{\bar{\eta}}_t)}{dt} = \gamma_t \Delta\bar{\eta}_t + \beta_t
		\qquad \Delta{\bar{\eta}}_T = \lambda \bar{\eta}_T^{MFG} - \bar{\eta}_T^{MKV}
	\end{equation*}
	with coefficients 
	\begin{equation*}
	\left\{
		\begin{array}{rcl}
			\gamma_t &=& \displaystyle -2 b_1 - 2\bar{b}_1 + \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \left(\lambda \bar{\eta}_t^{MFG} + \bar{\eta}_t^{MKV} \right),\\
			\beta_t &=& \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q + \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)).
		\end{array}
	\right.
	\end{equation*} 
	Since $q_T + \bar{q}_T(1-s_T)^2 = \bar{\eta}_T^{MKV}$ and $\lambda \bar{\eta}_0^{MFG} - \bar{\eta}_0^{MKV} = \Delta\bar{\eta}_0$, we deduce from the two equations in (\ref{eq:SC_MFG_MKV_2}) that:
	\begin{equation*}
		\begin{split}
			& SC^{MFG} - SC^{MKV}\\
			=& \frac{1}{2} \left[ \Delta\bar{\eta}_0 \bar{x}_0^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
			=& \frac{1}{2} \int_0^T \left[ - \frac{d (\Delta\bar{\eta}_t (\bar{x}_t^{MFG})^2) }{dt}  + \left( 	\frac{d( \Delta{\bar{\eta}}_t)}{dt} - \gamma_t \Delta\bar{\eta}_t  \right)(\bar{x}_t^{MFG})^2 \right] dt\\
			=& \frac{1}{2}\int_0^T \left[- 2\Delta{\bar{\eta}}_t \bar{x}_t^{MFG} \dot{\bar{x}}_t^{MFG} - \gamma_t \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \right]dt \\
			=& \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}) - \gamma_t)\right] dt\\
			=& \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt
		\end{split}
	\end{equation*}
	where we use the relationship $\dot{\bar{x}}_t = (a^x+a^{\bar{x}}+(a^y+a^{\bar{y}})\bar{\eta}_t)\bar{x}_t$ (see Appendix \ref{appendix_solving_fbsdes}) for the fourth equality.

@@

We study in the following the variation of $PoA$ by letting one of the coefficients tends to $0$ or to $\infty$. It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
    \begin{equation}
		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0 \qquad u_T = D^u
		\label{eq:riccati_ut}
	\end{equation}	
	\begin{equation}
	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0 \qquad w_T = D^w
	\label{eq:riccati_wt}
	\end{equation}
	\begin{equation}
	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0 \qquad \eta_T = D^\eta
	\label{eq:riccati_etat}
	\end{equation}
	where
	\begin{IEEEeqnarray*}{rClcrClcrCl}
		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right) & \qquad & 
		A^w &=& - (b_1 + \bar{b}_1) & \qquad & 
		A^\eta &=& - b_1 \nonumber \\
		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} & \qquad &	
		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} &\qquad & 
		B^\eta &=& \frac{b_2^2}{r+ \bar{r}} \nonumber \\
		C^u &=& \lambda (q + \bar{q}(1-s))& \qquad & 
		C^w &=& q + \bar{q}(1-s)^2 & \qquad &
		C^\eta &=& q + \bar{q} \nonumber \\
		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)) & \qquad & 
		D^w &=& q_T + \bar{q}_T(1-s_T)^2 & \qquad & 
		D^\eta &=& q_T + \bar{q}_T 
	\end{IEEEeqnarray*}
If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
\begin{equation}
		u_t= \frac{-(C^u+D^u \delta^+_u) + (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(\delta^-_u - D^u B^u) - (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}
	\label{eq:riccati_ut_sol}
\end{equation}
where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. We have analogous expressions for $w_t$ and $\eta_t$ in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$.

@@

	By taking the limit $b_2 \to 0$, we have $\delta^\pm_u = -A^u \pm \vert A^u \vert $ and $\delta^{+}_u - \delta^{-}_u = 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce
	$$u_t \xrightarrow[b_2 \to 0 ]{} 0, \quad \forall t \in [0,T].$$
	This implies that $\bar{x}_t^{MFG} \to \bar{x}_0 \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$.

>>>>

We consider a system of $N$ players whose private states are denoted at time $t$ by $X^1_t$, $X^2_t$, $\cdots$, $X^N_t$. To keep the presentations simple, we assume the state space is $\mathbb{R}$. We denote by $\mu^N_t$ the empirical distribution of the states, namely
\begin{equation*}
\mu^N_t=\frac1N\sum_{i=1}^N\delta_{X^i_t}.
\end{equation*}
We assume that these states evolve in continuous time under the influences of controls  $\alpha^1_t$, $\alpha^2_t$, $\cdots$ , $\alpha^N_t$ $\in \mathbb{A}$, where the set of admissible controls, $\mathbb{A}$, will be defined later. Let $\nu^N_{t}$ denote the empirical measure of the controls:
\begin{equation*}
\nu^N_t=\frac1N\sum_{i=1}^N\delta_{\alpha^i_t}.
\end{equation*}
We also assume that if and when interactions between these states and controls are present, they are of a mean field type, i.e. through $\mu^N_t$ and $\nu^N_t$. The time evolution of the state for player $i$ is given by the It\^{o} dynamics:
\begin{equation*}
    dX^i_t=b(t,X^i_t,\mu^N_t,\alpha^i_t,\nu^N_t)dt+\sigma dW_t.
\end{equation*}
We work over the interval $[0,T]$ limited by a finite time horizon $T \in \mathbb{R}^+$. We assume the drift function $b:[0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A}) \ni (t,x,\mu,\alpha,\nu)  \rightarrow \mathbb{R}$ is Lipschitz in each of it's inputs. For the sake of simplicity, we assume that the volatility, $\sigma$, is a positive constant.

\subsubsection*{\textbf{Cost Functionals}}
We assume that we are given two functions $f:[0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A}) \ni (t,x,\mu,\alpha, \nu) \rightarrow \mathbb{R}$ and $g:\mathbb{R}\times \cP(\mathbb{R}) \ni (x,\mu) \rightarrow \mathbb{R}$ which we call running and terminal cost functions, respectively. We assume $f$ and $g$ are Lipschitz in each of their arguments. The goal of player $i$ is to minimize its expected cost as given by:
\begin{equation*}
J^i(\balpha^1,\cdots,\balpha^N)=\EE\bigg[\int_0^Tf(t,X^i_t,\mu^N_{t},\alpha^i_t,\nu^N_{t})\,dt +g(X^i_T,\mu^{N}_{T})\bigg].
\end{equation*}

@@

\subsection{\textbf{Nash Equilibrium: Mean Field Game Formulation}}
\label{sub:MFG_formulation}
The goal of this subsection is to articulate what is meant by a feedback function providing a mean field game equilibrium. To begin, we define what we call the \textit{mean field environment}. By symmetry of the players, we suppose all of the players in the mean field game use the same feedback function, $\phi$. Then the \textit{mean field environment} specified by $\phi$ is characterized by $\cL(X^{\phi}_t)_{0\le t\le T}$ and $\cL(\phi(t,X^{\phi}_t))_{0\le t\le T}$ where the dynamics of $(X^{\phi}_t)_{0\le t\le T}$ are given by equation (\ref{eq:X}). Since we search for a Nash equilibrium, we consider a representative agent who wishes to find their best response, $\phi'$, to the mean field environment specified by $\phi$, in which case their state is given by $\boldsymbol{X^{\phi',\phi}}=(X^{\phi',\phi}_t)_{0\le t\le T}$ solving the standard stochastic differential equation:
\begin{equation*}
    dX^{\phi',\phi}_t=b(t,X^{\phi',\phi}_t,\cL(X^{\phi}_t),\phi'(t,X^{\phi',\phi}_t),\cL(\phi(t,X^{\phi}_t)))dt+\sigma dW_t.
\end{equation*}
Consider the function:
\begin{equation*}
    \cS(\phi',\phi)=\biggl[\int_0^T<f(t,\cdot,\cL(X^{\phi}_t),\phi'(t,\cdot),\cL(\phi(t,X^{\phi}_t)),\cL(X^{\phi',\phi}_t))> dt +<g(\cdot,\cL(X^{\phi}_T)),\cL(X^{\phi',\phi}_t)>\biggr].
\end{equation*}
The best response for the representative agent in the mean field environment specified by $\phi$ is the feedback function minimizing this cost, namely $\phi^*=\arg\inf_{\phi'}\cS(\phi',\phi)$. Assuming the minimizer is unique (which will be the case for the models we consider), this defines a mapping $\Phi:\phi \rightarrow \phi^*$. If there is a $\hat{\phi}$ such that $\Phi(\hat{\phi})=\hat{\phi}$, then the players are in a mean field game equilibrium.

Thus, the search for a feedback function providing a mean field game equilibrium can be summarized as the following set of two successive steps:
\begin{enumerate}
\item For each feedback function $\phi:[0,T] \times \mathbb{R} \ni (t,x) \rightarrow \mathbb{R}$, solve the optimal control problem
\begin{equation*}
    \phi^*=\arg \inf_{\phi'}\cS(\phi',\phi).
\end{equation*}
Define the mapping $\Phi(\phi):=\phi^*$.
\item Find a fixed point $\hat{\phi}$ of $\Phi$ such that $\Phi(\hat{\phi})=\hat{\phi}$.
\end{enumerate}

When these two steps can be taken successfully, we say that $\hat{\phi}$ provides a mean field game equilibrium. Note that $\boldsymbol{X^{\hat{\phi},\hat{\phi}}}=\boldsymbol{X^{\hat{\phi}}}$ and therefore $\cS(\hat{\phi},\hat{\phi})=SC(\hat{\phi})$ gives the social cost for the mean field game equilibrium provided by $\hat{\phi}$. Notice that there could possibly be many feedback functions providing a mean field game equilibrium. Let $\mathcal{N}$ denote the set of all such feedback functions providing mean field game equilibria, as detailed above, i.e.
\begin{equation*}
    \mathcal{N}=\{\phi:[0,T] \times \mathbb{R} \ni (t,x) \rightarrow \mathbb{R}\ |\ \Phi(\phi)=\phi \}.
\end{equation*}

@@

\begin{equation*}
\begin{split}
    dY_t&=- \partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)dt+Z_tdW_t \\
    Y_T&=\partial_xg(X_T, \cL(X_T)).
\end{split}
\end{equation*}
According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,y)=0$. We introduce the function:
\begin{equation*}
    \hat{\alpha}(t,x,\bar{\mu},\bar{\nu},y)=\frac{\bar{r}(t)\bar{s}(t)\bar{\nu}-b_2(t)y}{r(t)+\bar{r}(t)},
\end{equation*}
and use the control $\hat{\alpha}_t=\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$. When solving the fixed point step, we identify $\bar{\nu}_t=\mathbb{E}(\hat{\alpha}_t)$. By taking the expectation, we find:
\begin{equation*}
    \mathbb{E}(\hat{\alpha}_t)=c^{MFG}(t)\mathbb{E}(Y_t)
\end{equation*}
with:
\begin{equation*}
    c^{MFG}(t)=-\frac{b_2(t)}{r(t)+\bar{r}(t)(1-\bar{s}(t))}.
\end{equation*}
Thus, necessarily we must have:
\begin{equation*}
    \hat{\alpha}_t=a^{MFG}(t) Y_t+b^{MFG}(t)\mathbb{E}(Y_t)
\end{equation*}
with:
\begin{equation*}
    a^{MFG}(t)=-\frac{b_2(t)}{r(t)+\bar{r}(t)},
\end{equation*}
and:
\begin{equation*}
    b^{MFG}(t)=-\frac{\bar{r}(t)\bar{s}(t)b_2(t)}{(r(t)+\bar{r}(t))(r(t)+\bar{r}(t)(1-\bar{s}(t)))}.
\end{equation*}
Note that $c^{MFG}(t)=a^{MFG}(t)+b^{MFG}(t)$. The solution of the mean field game equilibrium problem is given by the solution to the FBSDE system:
\begin{equation}
\begin{split}
        dX_t&=\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MFG}(t)b_2(t)Y_t+(b^{MFG}(t)b_2(t)+c^{MFG}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
        dY_t&=-\left((q(t)+\bar{q}(t))X_t-\bar{q}(t)s(t)\mathbb{E}X_t+b_1(t)Y_t \right)dt +Z_t dW_t
\end{split}
\label{eq:FBSDE_EMFG}
\end{equation}
with initial condition $X_0=\xi$, a random variable with finite mean and variance, and terminal condition $Y_T=(q_T+\bar{q}_T)X_T-\bar{q}_Ts_T\mathbb{E}X_T$.

@@

\begin{proposition}
	Under assumption (\ref{eq:assumptions}), the difference in the social costs in the LQEMFG and LQEMKV problems can be represented by
	\begin{equation*}
		\Delta SC := SC^{MFG} - SC^{MKV} =  \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt.
	\end{equation*}
\label{prop:diff_SC}
\end{proposition}
\begin{proof}
	The solutions $\bar{\eta}^{MFG}_t$ and $\bar{\eta}^{MKV}_t$ for the associated Riccati equations are well defined under assumption (\ref{eq:assumptions}). We notice that $\Delta\bar{\eta}_t$ defined in (\ref{eq:delta_eta}) satisfies the following first-order differential equation:
	\begin{equation*}
		\frac{d( \Delta{\bar{\eta}}_t)}{dt} = \gamma_t \Delta\bar{\eta}_t + \beta_t
		\qquad \Delta{\bar{\eta}}_T = \lambda \bar{\eta}_T^{MFG} - \bar{\eta}_T^{MKV}
	\end{equation*}
	with coefficients 
	\begin{equation*}
	\left\{
		\begin{array}{rcl}
			\gamma_t &=& \displaystyle -2 b_1 - 2\bar{b}_1 + \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \left(\lambda \bar{\eta}_t^{MFG} + \bar{\eta}_t^{MKV} \right),\\
			\beta_t &=& \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q + \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)).
		\end{array}
	\right.
	\end{equation*} 
	Since $q_T + \bar{q}_T(1-s_T)^2 = \bar{\eta}_T^{MKV}$ and $\lambda \bar{\eta}_0^{MFG} - \bar{\eta}_0^{MKV} = \Delta\bar{\eta}_0$, we deduce from the two equations in (\ref{eq:SC_MFG_MKV_2}) that:
	\begin{equation*}
		\begin{split}
			& SC^{MFG} - SC^{MKV}\\
			=& \frac{1}{2} \left[ \Delta\bar{\eta}_0 \bar{x}_0^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
			=& \frac{1}{2} \int_0^T \left[ - \frac{d (\Delta\bar{\eta}_t (\bar{x}_t^{MFG})^2) }{dt}  + \left( 	\frac{d( \Delta{\bar{\eta}}_t)}{dt} - \gamma_t \Delta\bar{\eta}_t  \right)(\bar{x}_t^{MFG})^2 \right] dt\\
			=& \frac{1}{2}\int_0^T \left[- 2\Delta{\bar{\eta}}_t \bar{x}_t^{MFG} \dot{\bar{x}}_t^{MFG} - \gamma_t \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \right]dt \\
			=& \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}) - \gamma_t\right] dt\\
			=& \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt
		\end{split}
	\end{equation*}
	where we use the relationship $\dot{\bar{x}}_t = (a^x+a^{\bar{x}}+(a^y+a^{\bar{y}})\bar{\eta}_t)\bar{x}_t$ (see Appendix \ref{appendix_solving_fbsdes}) for the fourth equality.

@@

We study in the following the variation of $PoA$ by letting one of the coefficients tend to $0$ or to $\infty$. It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
    \begin{equation}
		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0 \qquad u_T = D^u
		\label{eq:riccati_ut}
	\end{equation}	
	\begin{equation}
	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0 \qquad w_T = D^w
	\label{eq:riccati_wt}
	\end{equation}
	\begin{equation}
	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0 \qquad \eta_T = D^\eta
	\label{eq:riccati_etat}
	\end{equation}
	where
	\begin{IEEEeqnarray*}{rClcrClcrCl}
		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right) & \qquad & 
		A^w &=& - (b_1 + \bar{b}_1) & \qquad & 
		A^\eta &=& - b_1 \nonumber \\
		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} & \qquad &	
		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} &\qquad & 
		B^\eta &=& \frac{b_2^2}{r+ \bar{r}} \nonumber \\
		C^u &=& \lambda (q + \bar{q}(1-s))& \qquad & 
		C^w &=& q + \bar{q}(1-s)^2 & \qquad &
		C^\eta &=& q + \bar{q} \nonumber \\
		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)) & \qquad & 
		D^w &=& q_T + \bar{q}_T(1-s_T)^2 & \qquad & 
		D^\eta &=& q_T + \bar{q}_T 
	\end{IEEEeqnarray*}
If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
\begin{equation}
		u_t= \frac{-(C^u+D^u \delta^+_u) + (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(\delta^-_u - D^u B^u) - (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}
	\label{eq:riccati_ut_sol}
\end{equation}
where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. We have analogous expressions for $w_t$ and $\eta_t$ in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$.

@@

	By taking the limit $b_2 \to 0$, we have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce
	$$u_t \xrightarrow[b_2 \to 0 ]{} 0, \quad \forall t \in [0,T].$$
	This implies that $\bar{x}_t^{MFG} \to \bar{x}_0 \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$.
